### 2010-07-02 paper/IIWAS2010/content/abstract.tex
latest version
The submitted copy of the paper

The Morpheus question answering system uses deep web search to answer user queries. Queries are represented by a semi-structured format that contains query terms and referenced classes within a specific ontology.  Morpheus answers questions by using methods from prior successful searches.  The system ranks stored methods based on a similarity quasi-metric defined on assigned classes of queries. Similarity depends on the class heterarchy in an ontology and its associated text corpora. Finally, Morpheus revisits the prior search pathways of the stored searches to construct possible answers. The realm-based ontologies are created using Wikipedia pages, associated categories, and the synset heterarchy of WordNet. This paper describes the entire process with emphasis on the matching of user queries to stored answering methods.

>>>>

When users search the deep web, the essence of their search is often found in a previously answered query. The Morpheus question answering system reuses prior searches to answer similar user queries. Queries are represented in a semi-structured format that contains query terms and referenced classes within a specific ontology.  Morpheus answers questions by using methods from prior successful searches.  The system ranks stored methods based on a similarity quasi-metric defined on assigned classes of queries. Similarity depends on the class heterarchy in an ontology and its associated text corpora. Morpheus revisits the prior search pathways of the stored searches to construct possible answers. The realm-based ontologies are created using Wikipedia pages, associated categories, and the synset heterarchy of WordNet. This paper describes the entire process with emphasis on the matching of user queries to stored answering methods.

### 2010-07-02 paper/IIWAS2010/content/introduction.tex
The submitted copy of the paper

When traveling though a jungle to a destination, it is easy to get lost.  The first person to journey somewhere may make a number of mistakes when trying to find the best path to their destination. Those who come later find it easier to reach the destination if a well-marked trail has been created. Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating a user's discovery experience as a unique entity, one can exploit the fact that a similar search may have already been performed.  In one study, almost 40 percent of all queries were repetitions of previous queries \cite{1277770}. Thus, reuse of prior searches is one way to optimize the search
process.  Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer to a user query. Morpheus follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.

Morpheus focuses on the deep (or hidden) web to answer questions because its scale and database driven property implies the existence of huge stores of quality information \cite{1453931}.  Web forms act as an interface to this information.  Morpheus employs user exploration through these web forms to learn the types of data each deep web location provides.

There are two distinct Morpheus user roles. A \textit{path-finder} enters queries in the Morpheus web interface and searches for an answer to the query using an instrumented web browser. This web tracking tool stores the query and necessary information to revisit the pathways to the page where the path-finder found the answer. A \textit{path-follower} uses the Morpheus system much like a regular search engine with a natural language interface. The path-follower enters a question in a text box and receives a guided path to the answer. The system exploits previously found paths to provide an answer.

Morpheus represents user-query details in a semi-structured query (SSQ). It assumes the query terms belong to classes of a \textit{consistent} realm-based ontology, that is, one having a singly rooted heterarchy whose subclass/superclass relations have meaningful semantic interpretations. When a path-follower enters a query, Morpheus ranks SSQs in the store based on class similarity. Suppose a path follower asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In this query the classes associated with terms, e.g. \emph{Manufacturer} with \emph{Toyota}, help us identify similar queries.

>>>>

When traveling though a jungle to a destination, it is easy to get lost.  The first person to journey somewhere may make a number of mistakes when trying to find the best path to their destination. Those who come later find it easier to reach the destination if a well-marked trail has been created. Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating a user's discovery experience as a unique entity, one can exploit the fact that a similar search may have already been performed.  In one study, almost 40 percent of web queries were repetitions of previous queries \cite{1277770}. Thus, reuse of prior searches is one way to optimize the search process.  Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer to a user query. Morpheus follows path finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.

Morpheus focuses on the deep (or hidden) web to answer questions because of the large stores of quality information provided by the databases that support it \cite{1453931}.  Web forms act as an interface to this information.  Morpheus employs user exploration through these web forms to learn the types of data each deep web location provides.

There are two distinct Morpheus user roles. A \emph{path finder} enters queries in the Morpheus web interface and searches for an answer to the query using an instrumented web browser. This web tracking tool stores the query and necessary information to revisit the pathways to the page where the path finder found the answer. A \emph{path follower} uses the Morpheus system much like a regular search engine with a natural language interface. The path follower enters a question in a text box and receives a guided path to the answer. The system exploits previously found paths to provide an answer.

Morpheus represents a user question as a semi-structured query (SSQ). It assumes the query terms belong to classes of a \emph{consistent} realm-based ontology, that is, one having a singly rooted heterarchy whose subclass/superclass relations have meaningful semantic interpretations. When a path follower enters a query, Morpheus ranks SSQs in the store based on class similarity. Suppose a path follower asks: \emph{ A 1997 Toyota Camry V6 needs what size tires?} In this query the classes associated with terms, e.g. \emph{Manufacturer} with \emph{Toyota}, help us identify similar queries.

### 2010-07-02 paper/IIWAS2010/content/related_work.tex
The submitted copy of the paper

Several community QA systems have been developed, such as Yahoo! Answers \cite{yahooanswers2008}. These sites enlist a community of users to answer questions posed by other users.  This idea has led to socially integrated QA systems such as Aardvark \cite{vark2010}. In addition to having questions answered by users, Aardvark can contact potential question answerers through media beyond web pages (e.g. instant messages, mobile phones).  This allows for faster responses to questions.  Morpheus relies on both its user interface and referencing similar questions previously answered.

@@

The DBpedia\footnote{http://dbpedia.org} project is based on a community of contributors extracting semantic information from the Wikipedia and making this information available on the Web.  Wikipedia semantics includes info-box templates, categorization information,  images, geo-coordinates, links to external web pages, disambiguation pages, and redirects to pages in Wiki markup form \cite{Bizer2009}.  DBpedia does not define any new relations between the Wikipedia categories.

@@

YAGO is a semi-automatically constructed ontology obtained from the Wikipedia pages, info-boxes, categories, and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy \cite{Suchanek2009phd}. YAGO uses the Wikipedia page \emph{titles} as its ontology \emph{individuals} and \emph{categories} as its ontology \emph{classes}. YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives.  YAGO discovers connections between WordNet synsets and Wikipedia categories, parsing the category names and matching the parsed category components with the WordNet synsets.  Wikipedia categories having no WordNet match are ignored in the YAGO ontology.  The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets.

We use YAGO's principles to construct ontologies that provide similarity measures for answering questions within the same domain.  Thus far, these ontologies can be used to classifiy terms, however their classes do not always appropriately categorize query parameters.  Therefore, we are researching XXX in order to XXX.% TODO - fill in the XXX

>>>>

Several community QA systems have been developed, such as Yahoo! Answers \cite{yahooanswers2008}. These sites enlist a community of users to answer questions posed by other users.  This idea has led to socially integrated QA systems such as Aardvark \cite{vark2010}. In addition to having questions answered by users, Aardvark can contact potential question answerers through media beyond web pages (e.g. instant messages, mobile phones).  This allows for faster responses to questions.  Morpheus relies on its user interface and referencing previously answered questions.

@@

The DBpedia\footnote{http://dbpedia.org} project is a community of contributors extracting semantic information from Wikipedia and makes this information available on the Web. Wikipedia semantics includes info-box templates, categorization information,  images, geo-coordinates, links to external web pages, disambiguation pages, and redirects to pages in Wiki markup form \cite{Bizer2009}.  DBpedia does not define any new relations between the Wikipedia categories.

@@

YAGO is a semi-automatically constructed ontology obtained from the Wikipedia pages, info-boxes, categories, and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy \cite{Suchanek2009phd}. YAGO uses the Wikipedia page \emph{titles} as its ontology \emph{individuals} and \emph{categories} as its ontology \emph{classes}. YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives.  YAGO discovers connections between WordNet synsets and Wikipedia categories, parsing the category names and matching the parsed category components with the WordNet synsets. Each Wikipedia category not having a WordNet match is ignored in the YAGO ontology.  The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets.

We use YAGO's principles to construct ontologies that provide similarity measures for answering questions within the same domain.  Thus far, these ontologies can be used to classifiy terms, however their classes do not always appropriately categorize query parameters.  It is necessary to provide an appropriate level of class granularity.  Therefore, we are investigating  methods of identifying classes and their instances from deep web forms and documents.

### 2010-07-02 paper/IIWAS2010/content/results_discussion.tex
The submitted copy of the paper

First, we created an ontology for the automotive realm exploiting the Wikipedia pages, categories, and WordNet synsets. For each of the classes in the ontolgy we built corpora from the corresponding Wikipedia pages. Table describes the question answering process for the user query, ``A 1997 Toyota Camry V6 needs what size tires?''

%% TODO - need to refer back to the table which is figure one.
The Morpheus NLP engine parses this query into the constructs: WH:what,
Descriptive Information:1997 Toyota Camry V6, Asking For:size tires. From the
descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997
Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6. For
each of the terms, we determined relevant categories (non-increasing order of
relevance) from the ontology corpora. Table \ref{tbl:term_categories} shows
the top categories and their probabilities for each of the query term:

\begin{table}[h]\footnotesize

\begin{tabular}{| p{3.2cm} | l | r |}
\hline 
Term & Category & $P(Category|Term)$ \\ \hline
1997 & Sedans & 404132.77e-14\\ 
1997 Toyota & Engines & 7.90e-14\\ 
Toyota  & Sedans & 3486670.15e-14\\ 
Toyota Camry & Sedans & 12147.23e-14\\ 
Toyota Camry V6 & Coupes & 13.80e-14\\ 
Camry & Sedans & 312034.20e-14\\ 
Camry V6 & Coupes & 13.80e-14\\ 
V6 & Sedans & 4464535.40e-14\\ \hline
\end{tabular}

\caption{Terms' top categories and probabilities}
\label{tbl:term_categories}

@@

We found the top category of the terms in the candidate SSQ and determined the category divergence with the qualified SSQ classes in the QRM store. Then, we combined the divergence measure and
ranked QRMs based on the relevance score. Table \ref{tbl:ranked_queries} shows the top ranked SSQ for the query.  Finally, we execute the selected QRM and display the results to the user.

\begin{table}[h]\footnotesize

\begin{tabular}{| p{3.5cm} | p{3cm} | r |}
\hline
Query & Tagged Classes & Score\\ \hline
A 1997 Toyota Camry V6 needs what size tires? & IC:Sedans, Cars, Engines, Manufactures OC:size tires & 0.91\\ \hline 
What is the tire size for a 1998 Sienna XLE Van? & IC:Vans, Manufactures OC: tire size & 0.72\\ \hline 
Where can I buy a headlight for a Toyota Camry V6? & IC:Manufactures, Sedans, Engines OC: where & - \\ \hline 
What is the cost of a Toyota Camry V6 muffler? &  IC:Manufactures, Sedans, Engines OC: the clost  & - \\ \hline
\end{tabular}

\caption{Top ranked queries and relevance scores: IC - input classes, OC - output classes}
\label{tbl:ranked_queries}

@@

In this paper, we propose a novel question answering system that uses the deep web and previously answered user queries to answer similar questions. The system uses a path finder to annotate answer paths so path followers can discover answers to similar questions.  Each $(question, answer)$ pair is assigned a realm, and new questions are matched to the new $(question, answer)$ pairs. Classification of terms into classes is based on term frequency distributions in our corpora of web documents. We are investigating improvements to our solution by an approach similar to Topic Models \cite{Blei2003latentdirichlet}.

Manually forming a corpus of wilipedia pages associated with a class is a cumbersome task. Topic Modeling provides a promising approach to identifying pages relevent to given class in a more automated manner.
%The Wikipedia page categories has limitations. Without supervision, the page categorization is often a challenging problem, because topics in the pages that belong to a realm (e.g. automotive) usually overlap. So we are evaluating the applicability of probabilistic topic models to web page categorization, and automatic generation of a realm-ontology based on the topics being extracted.

>>>>

First, we built an ontology for the vehicular realm exploiting the Wikipedia pages, DBpedia categories, and WordNet synsets. For each of the classes in the ontolgy we built corpora from the corresponding Wikipedia pages. Figure \ref{fig:vehicular_ontology} shows a subsection of this ontology.

In Table \ref{tbl:nlp_engine_parse} we show the data that is output by the Morpheus NLP engines parse of the query.  It extracts the \emph{wh}-term that identifies the sentence as a question, identifies the answer class, and locates descriptive phrases that can be used to identify the answer. Finally, the engine produces n-grams from the phrases in the descriptive information sections.

Using the data in Table \ref{tbl:nlp_engine_parse} we determine relevant classes in non-increasing order of relevance. Table \ref{tbl:term_classes} shows the top classes and their probabilities for automotive queries.

\begin{table}[!]\footnotesize
	\begin{tabular}{|l|p{4.2cm}|}
		\hline 
		\emph{wh}-term & what \\
		\hline 
		descriptive phrases & \small 1997 Toyota Camry V6 \\
		\hline 
		asking for & size tires \\
		\hline 
		n-grams & \small 1997, 1997 Toyota, 1997 Toyota Camry, Toyota, Toyota Camry, Toyota Camry V6, Camry, Camry V6, V6 \\
		\hline
	\end{tabular}
	\caption{The output of NLP engine parse}
	\label{tbl:nlp_engine_parse} 
\end{table}

\begin{table}[!]\footnotesize

\begin{tabular}{| p{3.2cm} | l | r |}
\hline 
Term & Class & $P(Class|Term)$ \\ \hline
1997 & Sedans & 404132.77e-14\\ 
1997 Toyota & Engines & 7.90e-14\\ 
Toyota  & Sedans & 3486670.15e-14\\ 
Toyota Camry & Sedans & 12147.23e-14\\ 
Toyota Camry V6 & Coupes & 13.80e-14\\ 
Camry & Sedans & 312034.20e-14\\ 
Camry V6 & Coupes & 13.80e-14\\ 
V6 & Sedans & 4464535.40e-14\\ \hline
\end{tabular}

\caption{Terms' top classes and probabilities}
\label{tbl:term_classes}

@@

We found the top class of the terms in the candidate SSQ and determined the class divergence with the qualified SSQ classes in the QRM store. Then, we combined the divergence measure and ranked QRMs based on the relevance score. Table \ref{tbl:ranked_queries} shows the top ranked SSQ for the query. Finally, we execute the best QRMs and display the results to the user.

\begin{table}[!]\footnotesize

\begin{tabular}{| p{3.5cm} | p{3cm} | r |}
	\hline
	Query & Tagged Classes & Score\\ 
	\hline
	\small A 1997 Toyota Camry V6 needs what size tires? & \small Sedan, Automobile, Engine, Manufacturer & 0.91\\ 
	\hline 
	\small What is the tire size for a 1998 Sienna XLE Van? & \small Van, Manufacturer & 0.72\\
	\hline 
	\small Where can I buy an engine for a Toyota Camry V6? & \small Sedan, Automobile Engine, Manufacturers & 0.74 \\
	\hline 
%What is the cost of a Toyota Camry V6 muffler? &  IC:Manufactures, Sedans, Engines OC: the clost  & 0.97 \\ \hline
\end{tabular}

\caption{Top ranked queries}
\label{tbl:ranked_queries}

@@

In this paper, we propose a novel question answering system that uses the deep web and previously answered user queries to answer similar questions. The system uses a path finder to annotate answer paths so path followers can discover answers to similar questions.  Each (\emph{question, answer path}) pair is assigned a realm, and new questions are matched to existing (\emph{question, answer path}) pairs. Classification of new question terms into classes is based on term frequency distributions in our realm specific corpora of web documents.  These terms are the input to existing answer paths and we re-execute these paths with the new input to produce results.

Manually forming a corpus of Wikipedia pages associated with a class is a cumbersome task. Topic modeling provides a promising approach to identifying pages relevant to a given class in a more automated manner \cite{Blei2003latentdirichlet}. We believe a mix between our web form entry annotation methods and form label extraction \cite{1453931} can yield promising results. Combining this with the method of Elmeleegy et al. \cite{1687749} may completely remove the user from the answer path generation process.

Additionally, we are investigating methods of merging QRMs to answer compound questions.  We will also chain QRMs using the principles of transform composition \cite{transformscout}.
